The CrypTool Script: \\ Cryptography, Mathematics and more \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (8th edition -- distributed with CrypTool version 1.4.10)} \vspace{60pt}

### 2007-06-05 script/en/chapters/primes.tex
Skript: updates, C307 Engl, mutual links)

\hline
\end{tabular}
\caption{The 20 largest known primes and its particular number types
         (as of May 2007)}    % Eyecatcher_neue-Mersenne
\label{L_n_Largest_Kown-Primes}
\end{center}
\end{table} 
\footnotetext{\index{Number!Sierpinski}\index{Seventeen or Bust SoB}%
This number was found within the distributed computing project
``Seventeen or Bust'' (SoB) (\href{http://www.seventeenorbust.com}{\texttt{http://www.seventeenorbust.com}})
% {\href{http://www.mersenne.org} {\tt http://www.mersenne.org}}
at March 26, 2007. While the well known \hyperlink{GIMPS-project}{GIMPS project} (chapter~\ref{zahlentyp_mersenne}) searches for bigger and bigger of the infinitely many primes, there is a chance, that the SoB project could have been completed its
task sometime.

@@

% --------------------------------------------------------------------------
\vskip +10 pt
\subsubsection
   [Generalized Mersenne numbers $f(k,n) = k \cdot 2^n \pm 1$]
   {Generalized Mersenne numbers
   $f(k,n) = k \cdot 2^n \pm 1 $  for $ n $ prime and $ k $ small prime}
   \label{generalized-mersenne-no1}
   For this first generalisation of the Mersenne 
   numbers\index{Mersenne!number!generalized}
   there are (for small $k$)
   also extremely quick prime number tests (see \cite{Knuth1981}). This can
   be performed in practice using software such as the Proths software from
   Yves Gallot\index{Gallot, Yves}
\vspace{-10pt}
\begin{itemize}
  \item[] {\href{http://www.prothsearch.net/index.html}
    {\tt http://www.prothsearch.net/index.html}}.
\end{itemize}

@@

   Details of this can be found at:
\vspace{-10pt}
\begin{itemize}
  \item[] \href{http://www.cerias.purdue.edu/homes/ssw/cun}
               {\tt http://www.cerias.purdue.edu/homes/ssw/cun}
\end{itemize}

>>>>

\hline
\end{tabular}
\caption{The 20 largest known primes and its particular number types
         (as of May 2007)}    % Eyecatcher_neue-Mersenne
\label{L_n_Largest_Known-Primes}
\end{center}
\end{table} 
\footnotetext{\index{Number!Sierpinski}\index{Seventeen or Bust SoB}%
This number was found within the distributed computing project
``Seventeen or Bust'' (SoB) (\href{http://www.seventeenorbust.com}{\texttt{http://www.seventeenorbust.com}})
% {\href{http://www.mersenne.org} {\tt http://www.mersenne.org}}
at March 26, 2007. While the well known \hyperlink{GIMPS-project}{GIMPS project} (chapter~\ref{zahlentyp_mersenne}) searches for bigger and bigger of the infinitely many primes, there is a chance, that the SoB project could have been completed its
task sometime.

@@

% --------------------------------------------------------------------------
\vskip +10 pt
\subsubsection
   [Generalized Mersenne numbers $f(k,n) = k \cdot 2^n \pm 1$ / Proth numbers]
   {Generalized Mersenne numbers
   $f(k,n) = k \cdot 2^n \pm 1 $  for $ n $ prime and $ k $ small prime
    / Proth numbers\footnotemark}
    \footnotetext{%
       Their names come from the French farmer FranÁois Proth (1852-1879).
       More famous as the Proth primes is the related Sierpinski 
       problem\index{Number!Sierpinski}: Find all numbers k, so that
       $k*2^n+1$ is composite for all n > 0.
       See table \ref{L_n_Largest_Known-Primes}.
    }
   \label{generalized-mersenne-no1}

   This first generalisation of the Mersenne
   numbers\index{Mersenne!number!generalized}
   creates the so called Proth numbers\index{Number!Proth}.
   There are (for small $k$) extremely quick prime number tests
   (see \cite{Knuth1981}). This can be performed in practice using software
   such as the Proths software from Yves Gallot\index{Gallot, Yves}:
\vspace{-10pt}
\begin{itemize}
  \item[] {\href{http://www.prothsearch.net/index.html}
            {\tt http://www.prothsearch.net/index.html}}.
\end{itemize}

@@

   Details of this can be found at:
\vspace{-10pt}
\begin{itemize}
  \item[] {\href{http://www.cerias.purdue.edu/homes/ssw/cun}
            {\tt http://www.cerias.purdue.edu/homes/ssw/cun}}
\end{itemize}
